\vspace{-15mm}\fontsize{24pt}{10pt}\selectfont\textbf{// All comments are NOT created equal}

### 2014-11-18 Proposal.tex
Updates to Introduction and general structure

 \section*{Abstract}

Visualization of knowledge is important to foster learning. To optimize the representation of knowledge and its interdependencies, we will focus on identifying ways to present knowledge without loosing context. This research aims at taking an existing annotated corpus and presenting its contents in a way that allows the audience to see the dependencies of the covered topics. This form of presenting the knowledge should make it easy to examine materials that form the basis for the topics the audience is interested in.\\

@@

If this research is successful one could envision connecting all of Mathematics or other fields in a way that allows students to go back to the concepts they have forgotten to understand the topics currently covered in class. As such it will foster learning and could transform how we interact with course material as a whole. It is easy to see that this research would also have many other real world applications anywhere where knowledge is supposed to be transferred.\\

@@

  (target size: 1 page)
\newpage
  \section{Statement and Motivation of Research}

  This part should make clear which question, exactly, you are
  pursuing, and why your project is relevant/interesting. This is the
  place to cite relevant literature. Where does your project extend
  the state of the art? what weaknesses in known approaches to you
  hope to overcome? If you have carried out preliminary experiments,
  describe them here.

What is the idea?
Why is this important for the world?

What is Prezi?
How will this improve learning?
What's the best representation one could do

  (target size: 3-5 pages)
\newpage
  \section{Planned Investigation}

@@

3. Planning
How will this be implemented?
Using which frameworks?

  (target size: 3-4 pages)
\newpage
  \section{Evaluation Criteria}

>>>>

 \section*{Abstract}
Visualization of knowledge is important to foster learning. To optimize the representation of knowledge and its interdependencies, we will focus on identifying ways to present knowledge without loosing context. This research aims at taking an existing annotated corpus and presenting its contents in a way that allows the audience to see the dependencies of the covered topics. This form of presenting the knowledge should make it easy to examine materials that form the basis for the topics the audience is interested in.\\

@@

The OMDoc (Open Mathematical Documents) format is a content markup scheme for mathematical documents. Using OMDoc, this research aims to visualize connecting some of what is written on Mathematics or other fields in a way that allows students to go back to the concepts they have forgotten to understand the topics currently covered in class. As such it will foster learning and could transform how we interact with course material as a whole. It is easy to see that this research would also have many other real world applications anywhere where knowledge is supposed to be transferred.\\

@@

  (target size: 1 page)
\newpage
  \section{Statement and Motivation of Research}
  This part should make clear which question, exactly, you are
  pursuing, and why your project is relevant/interesting. This is the
  place to cite relevant literature. Where does your project extend
  the state of the art? what weaknesses in known approaches to you
  hope to overcome? If you have carried out preliminary experiments,
  describe them here.

(target size: 3-4 pages)

\subsection{OMDoc}
(half a page)
\vspace*{8cm}
\subsection{Spatial Narration}
What is Prezi?
(half a page)
\vspace*{8cm}
\subsection{Combining OMDoc and Spatial Narration}
What is the idea?
(half a page)
\newpage
\subsection{Positive Effects of the Combination of Spatial Narration and OMDoc}
Why is this important for the world?
How will this improve learning?
(1 page)
\newpage
\subsection{Different Representations of Data}
What's the best representation one could do?
(1 page)
  (target size: 3-5 pages)
\newpage
\section{Planned Investigation}

@@

How will this be implemented?
Using which frameworks?

\subsection{Forming Visualizations out of Knowledge Graphs which Convey Meaning}
(1 page)
\newpage

\subsection{Ordered Knowledge Graphs}
(1 page)
\newpage

\subsection{Meaningful Representation of Knowledge Graphs}
(1 page)
\newpage

\section{Evaluation Criteria}

????
